Setting my wd and importing the data
```{r}
getwd()



# character vector csv files to read in

file_list <- list.files(pattern = ".csv")

#prints out all the datasets I downloaded for the weeks homework
file_list

#for each name access the file and store in a df

art <- read.csv(file = file_list[1], header= TRUE, sep = ",")

flowingdata <- read.csv(file = file_list[2], header= TRUE, sep = ",")

hotDogContest <- read.csv(file = file_list[3], header= TRUE, sep = ",")

hotDogPlaces <- read.csv(file = file_list[4], header= TRUE, sep = ",")

unemploymentRate <- read.csv(file = file_list[5], header= TRUE, sep = ",")

usPostage<- read.csv(file = file_list[6], header= TRUE, sep = ",")


worldPop <- read.csv(file = file_list[7], header= TRUE, sep = ",")



```


Making the plots
```{r}
# change margins so that our labels will appear


par(mar=c(5,6,4,1)+.1)



#the first plot


fill_colors <- c()
for ( i in 1:length(hotDogContest$Country) ) {
  if (hotDogContest$Country[i] == "United States") {
    fill_colors <- c(fill_colors, "#821122")
  } else {
    fill_colors <- c(fill_colors, "#cccccc")
  }
}

barplot(hotDogContest$Dogs.eaten, names.arg=hotDogContest$Year, col=fill_colors, space= 0.3, border= NA, xlab="Year", ylab="Hot dogs and buns (HDB) eaten", main= "Nathan's Hot Dog Eating Contest Results, 1980-2010", axis.lty=  )


#second plot
hotDogPlaces

names(hotDogPlaces) <- c("2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010")


hot_dog_matrix <- as.matrix(hotDogPlaces)

#place data into a matrix for stacked bar chart

barplot(hot_dog_matrix, border=NA, space=0.25, ylim=c(0, 200), xlab="Year", ylab="Hot dogs and buns (HDBs) eaten", main="Hot Dog Eating Contest Results, 1980-2010")


#third plot

plot(flowingdata$Subscribers, type="h", ylim=c(0, 30000),
     xlab="Day", ylab="Subscribers")
points(flowingdata$Subscribers, pch=19, col="black")

#fourth plot
plot(worldPop$Year, worldPop$Population, type="l",
     ylim=c(0, 7000000000), xlab="Year", ylab="Population")

#fifth plot
plot(usPostage$Year, usPostage$Price, type="s",
      main="US Postage Rates for Letters, First Ounce, 1991-
2010",
      xlab="Year", ylab="Postage Rate (Dollars)")


#sixth plot
scatter.smooth(x=1:length(unemploymentRate$Value),
               y=unemploymentRate$Value, ylim=c(0,11), degree=2, col="#CCCCCC", span=0.5)

Change setting so that our next plots will all appear on the same page

Looking at the distribution of sales in the art dataset.

```{r}

par(mfrow=c(2,2)) 

#first plot
boxplot(art$total.sale, horizontal =TRUE, main = "Boxplot Distribution Total Sales", xlab= "Total Sales", col = "yellow")



#second plot

hist(art$total.sale, breaks=10, main = "Histogram Distribution Total Sales", ylab = "volume of sales", xlab = "price per unit", col = "orange")

#subset the data
dfDraw    <- art[art$paper == "drawing",]

#create density of distribution
dfDrawd <- density(dfDraw$total.sale)

#plot the density distribution
plot(dfDrawd, main = "Distribution Drawing Paper Sales")

#fill the plot with color like paper for aesthetics

polygon(dfDrawd, col = "beige", border = "black") # beige = paper color

#show distribution by showing lines where occurances are
rug1 <- rug(dfDraw$total.sale, col = "black")


#fourth plot
dfWater    <- art[art$paper == "watercolor",]
Waterd <- density(dfWater$total.sale)
plot(Waterd, main ="Distribution Watercolor Sales", xlab = "price per unit", ylab= "density of sales")
polygon(Waterd, col = "lightblue", border = "black") # don't assign as variable just run command
Rug1 <- rug(dfWater$total.sale, col = "lightblue")



               
               
               
    
